How to compute the fusion product of MV cycles in type A

### 2021-02-18 draft.tex
joels changes

Fix $G = \GL_m$ and let $T\subset G$ be the maximal torus of diagonal matrices. 
% are there other possibilities?? :S 
Write $P$ for the character lattice of $T$. Identify $P\cong \ZZ^m$ so that the set of dominant weights $P_+$ is given by the set of partitions having at most $m$ nonzero parts. Set $\cO = \CC\xt$ and $\cK = \CC\xT$. We will also need the notation $\cO_s$ for the completion of the local ring $\CC[t]$ at $s\in\spec\CC$ and $\cK_s$ for its fraction field $\CC\xT[t-s]$. 
% TODO: given by or described by?
% 
Note that (by changing the local coordinate on $\spec\CC[t]$ to $t-s$) we can identify $\cO_s \cong \cO$ and $\cK_s\cong\cK$.

@@

\subsection{Lattices}
\label{ss:lat}
We will use the lattice model, so it is useful to recall the following definition.  Let $ R \subset K$ be two rings (usually, but not always, $K $ will be a field).  Let $ n \in \mathbb N$ and consider $ K^n $ as a $K$-module.   By restriction $ K^n$ can be viewed as an $R$-module.  An $R$-lattice in $ M$ is an $R$-submodule $ L \subset K^n$ such that $ L $ is a free rank $ n $ $R$-module and $ L \otimes_R K = K^n $.  Equivalently $ L = \Sp_R(v_1, \dots, v_n)$ where $ v_1, \dots, v_n$ are free generators of $K^n$.

The trivial lattice is $L_0 = R^n \subset K^n $.  The group $\GL_n(K) $ acts simply transitively on the set of $ R$-lattices in $K^n$ and we obtain a bijection between the set of such lattices and $\GL_n(K)/\GL_n(R)$.

We will be particularly interested in $\CC[t]$-lattices in $ \CC[t,t^{-1}]^n$.  Given such a lattice $ L $ and a point $ a \in \CC$, the specialization of $ L $ at $ a $ is defined as
$$
L(a) := L \otimes_{\CC[t]} \CC[[t-a]] \subset \CC((t-a))\,.
$$
In particular we say that $ L $ is trivial at $ a $ if $ L(a) = \CC[[t-a]]^n.$

@@

\acom{I think that MVy use this notation also:

\includegraphics[width=\textwidth]{img/Capture d’écran, le 2021-02-17 à 13.03.10.png}}

@@

\begin{itemize}
    \item The ordinary affine Grassmannian $\Gr = G(\cK)/G(\cO)$. It is described in modular terms by 
    $$
    \Gr = \{ (P, \varphi) : \text{$V$ is a rank $n$ vector bundle on $ \PP $, $\varphi : V \rightarrow V_0 $ on $ \PP \setminus \{0\} $} \} 
    $$
    where $V_0$ is the trivial rank $n$ vector bundle on $\PP$.

    We also have a lattice description 
    $$ 
    \Gr = \{ L \subset \CC^n \otimes_\cO \cK : \text{ $L$ is a $\cO$-lattice} \}
    $$
    % 
    \item For any $ s \in \CC $, the ordinary affine Grassmannian $\Gr_s = G(\cK_s)/G(\cO_s)$ at $ s $. It is described in modular terms by
    $$
    \Gr_s = \{ (P, \varphi) : \text{$V$ is a rank $n$ vector bundle on $ \PP $, $\varphi : V \rightarrow V_0 $ on $ \PP \setminus \{s\} $} \} 
    $$
    We also have a lattice description 
    $$ \Gr_s = \{ L \subset \CC^n \otimes_{\cO_s} \cK_s : \text{ $L$ is a $\cO_s$-lattice} \}
$$   
    \item The thick affine Grassmannian $\Gr^{\sf th} = G(\CC\xT[t^{-1}])/G(\CC[t])$. It is described in modular terms by
    $$
        \Grth = \{ (P, \varphi) : \text{$V$ is a rank $n$ vector bundle on $ \PP $, $\varphi : V \rightarrow V_0 $ on $ D_\infty $ } \} % (a disk centered at $ \infty$)
    $$
    where $D_\infty$ denotes a disk centered at $ \infty$.
    We also have a lattice description 
$$ 
\Gr^{\sf th} = \{ L \subset \CC^n \otimes_{\CC[t]} \CC((t^{-1})) : \text{ $L$ is a $\CC[t]$-lattice} \}
$$   
\jcom{Maybe write $\cK_\infty$ for $ \CC\xT[t^{-1}] $?  Also maybe change the ``thick'' notation''. I made a $\Grth$ macro, but I had no idea where to put it.}

    \item The (two point) Beilinson--Drinfeld Grassmannian $\pi : \Grbd\to \AA$ (with one point fixed at 0, and the second point $s$ varying away from $s = 0$).
    It is described in modular terms by
    {\small
    $$
    \Grbd = 
    % \begin{aligned}
        \left\{ 
            (P,\varphi,s) : V\text{ is a rank $n$ vector bundle on }\PP, \varphi : V \rightarrow V_0 \text{ on } \PP \setminus \{0, s\}  
        \right\} 
    % \end{aligned}
    $$}
    The fibre of $\Grbd \to \AA$ over $ s \in \AA $, for $ s \ne 0$, will be denoted $ \Gr_{0,s} $ and is given by
    $$ \Gr_{0,s} := \pi^{-1}(s) = G(\CC[t, t^{-1}, (t-s)^{-1})/G(\CC[t])$$

    We also have a lattice description 
    {\small
    $$ 
    \Grbd = 
    \{ L \subset \CC^n \otimes_{\CC[t]} \CC[t,t^{-1}], s \in \CC : \text{ $L$ is a $\CC[t]$-lattice 
    % , $L$ is 
    trivial at any $ a \ne 0, s$} \}
    $$}
    % 
\end{itemize}

These different versions of the affine Grassmannian are related as follows.  First there is an isomorphism $ \Gr \cong \Gr_s $ coming from the isomorphism $ \Ks \cong \cK$.

Second, we have a map $$ \Grbd \rightarrow \Grth $$ which is given in modular terms by restricting the trivialization to $ D_\infty$.  It is given in group-theoretic terms on the fibre over $ s $ by
$$
G(\CC[t, t^{-1}, (t-s)^{-1}])/ G(\CC[t]) \rightarrow G(\CC((t^{-1}))/G(\CC[t])
$$
Finally, it is given in lattice terms as the identity on the lattice and using the inclusion $\CC[t, t^{-1}, (t-s)^{-1}]^n \rightarrow \CC((t^{-1}))^n$ on the ambient spaces.

The fibres $ Gr_{0,s}$ of $ \Grbd \rightarrow \AA$ are given as follows
$$
\Gr_{0,s} \cong \begin{cases} \Gr \times \Gr_s, \  s \ne 0 \\
\Gr, \ s = 0.
\end{cases}
$$
This isomorphism is given in the lattice realization as
$$
L \mapsto (L(0), L(s))
$$
in the $ s \ne 0 $ case.

@@

\jcom{I thought that it would be good to introduce this operation now, since we will use it often in the paper. I don't know what notation we should use.}

Now fix dominant weights $ \lambda_i, \mu_i \in P_+$ of size $N_i$ ($i=1,2$) and their sum $ \lambda = \lambda_1 + \lambda_2 = \mu_1 + \mu_2$ of size $ N = N_1 + N_2$.

% 
\begin{itemize}
    % \item Weights $\mu_i\le\lambda_i$ of size $N_i$ ($i=1,2$) 
    % \item Their sums $\mu = \sum \mu_i \le \lambda = \sum\lambda_i$ of size $N = \sum N_i$
    \item The point $L_\lambda = t^\lambda G(\cO)$ in $\Gr$ 
    \item The orbit $\Gr^\lambda = G(\cO) L_\lambda$ and its closure $ \overline{\Gr}^\lambda = \cup_{\lambda' \le \lambda} \Gr^{\lambda'}$.
    \item The family $ \overline{\Gr}^{\lambda_1, \lambda_2} \rightarrow \AA$, defined by $ \overline{\Gr}^{\lambda_1, \lambda_2} = \overline{Gr}^{\lambda_1} * \overline{Gr}^{\lambda_2}$.  By construction the fibre of $ \overline{\Gr}^{\lambda_1, \lambda_2} $ over $ s \ne 0 $ is $ \overline{\Gr}^{\lambda_1} \times \overline{\Gr}^{\lambda_2}$.  By Zhu's theorem (\jcom{need ref}), the fibre over $ 0 $ is $ \overline{\Gr}^{\lambda_1 + \lambda_2}$.

    \item The slice $\Gr_\mu = G_1[t^{-1}]L_\mu$ to the orbit $\Gr^\lambda$
    \item The ``slice'' $\cW_\mu = G_1\xT[t^{-1}] t^\mu G(\CC[t])$ to the ``orbit'' $\Gr_\AA^{\lambda_1,\lambda_2}$ \acom{is not presented as a family}% $(\Grbd[2])^{\lambda_1,\lambda_2}$; replaced \cW_{\mu_1,\mu_2} = by Joel's not'n & def, seemingly independent of the decomposition of \mu; modified Joel's double bracket --- still confused over where W_\mu ought to live 
\end{itemize}
The following notation leaves the realm of affine Grassmannians and probably deserves its own subsection. E.g.\ ``nilpotent cones?''
\begin{itemize}
    \item The nilpotent and semi-nilpotent cones $\cN$ and $\cN_\AA$ (of matrices with eigenvalues in $\{0\}$ and $\{0,s\} \in \AA\times\AA$ resp.) 
    \item The slice $\TT_\mu$ to the orbit $\OO_\lambda$ 
    \item The ``family of slices'' $\TT_{\mu_1,\mu_2}^{\AA}$ to the ``family of orbits'' $\OO^{\AA}_{\lambda_1,\lambda_2}$ \acom{ok to describe as such?}
\end{itemize}

@@

@@

>>>>

Fix $G = \GL_m$ and let $T\subset G$ be the maximal torus of diagonal matrices. 
% are there other possibilities?? :S 
Write $P$ for the coweight lattice of $T$, so we have $P\cong \ZZ^m$.  The dominant weights of $ G $ is the set of $ \lambda = (\lambda_1, \dots, \lambda_m) $ such that $ \lambda_1 \ge \cdots \ge \lambda_m$.  We also need the notion of effective dominant coweight, which means those $ \lambda $ as above with $ \lambda_m \ge 0$.  So an effective dominant coweight $ \lambda $ is a partition of $ \lambda_1 + \cdots + \lambda_m$, which we call the size of $ \lambda$.

Set $\cO = \CC\xt$ and $\cK = \CC\xT$. We will also need the notation $\cO_s = \CC[[t-s]]$ for the completion of the local ring $\CC[t]$ at $s\in\spec\CC$ and $\cK_s$ for its fraction field $\CC\xT[t-s]$. 
% TODO: given by or described by?
% 
Note that (by changing the local coordinate on $\spec\CC[t]$ to $t-s$) we can identify $\cO_s \cong \cO$ and $\cK_s\cong\cK$.

Given a coweight $\mu \in P$ and $ s\in \CC$, we define $ (t-s)^\mu$ to be the diagonal matrix with entries $ (t-s)^{\mu_1}, \dots, (t-s)^{\mu_m}$

@@

\subsection{Lattices}
\label{ss:lat}
We will use the lattice model, so it is useful to recall the following definition.  Let $ R \subset K$ be two rings (usually, but not always, $K $ will be a field).  Let $ m \in \mathbb N$ and consider $ K^n $ as a $K$-module.   By restriction $ K^m$ can be viewed as an $R$-module.  An $R$-lattice in $ M$ is an $R$-submodule $ L \subset K^m$ such that $ L $ is a free rank $ m $ $R$-module and $ L \otimes_R K = K^m $.  Equivalently $ L = \Sp_R(v_1, \dots, v_m)$ where $ v_1, \dots, v_n$ are free generators of $K^m$.

The trivial lattice is $L_0 = R^m \subset K^m $.  The group $\GL_m(K) $ acts transitively on the set of $ R$-lattices in $K^m$, thus giving a bijection between the set of such lattices and $\GL_m(K)/\GL_m(R)$.

We will be particularly interested in $\CC[t]$-lattices in $ \CC(t)^m$.  Given such a lattice $ L $ and a point $ a \in \CC$, the specialization of $ L $ at $ a $ is defined as
$$
L(a) := L \otimes_{\CC[t]} \CC[[t-a]] \subset \CC((t-a))\,.
$$
We say that $ L $ is trivial at $ a $ if $ L(a) = \CC[[t-a]]^m.$

@@

\acom{I think that MVy use this notation also: }

%\includegraphics[width=\textwidth]{img/Capture d’écran, le 2021-02-17 à 13.03.10.png}}

@@

\begin{itemize}
    \item The ordinary affine Grassmannian $\Gr = G(\cK)/G(\cO)$. It is described in modular terms by 
    $$
    \Gr = \{ (P, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ D_0 $, $\varphi : V \rightarrow V_0 $ on $ D_0 \setminus \{0\} $} \} 
    $$
    where $V_0$ is the trivial rank $m$ vector bundle, and $ D_0$ is the formal disk centered at $ 0 \in \PP$.

    We also have a lattice description 
    $$ 
    \Gr = \{ L \subset \cK^m : \text{ $L$ is a $\cO$-lattice} \}
    $$
    % 
    \item For any $ s \in \CC $, the ordinary affine Grassmannian $\Gr_s = G(\cK_s)/G(\cO_s)$ at $ s $. It is described in modular terms by
    $$
    \Gr_s = \{ (P, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ D_s $, $\varphi : V \rightarrow V_0 $ on $ D_s \setminus \{s\} $} \} 
    $$
    We also have a lattice description 
    $$ \Gr_s = \{ L \subset \cK_s^m : \text{ $L$ is a $\cO_s$-lattice} \}
$$   
    \item The thick affine Grassmannian $\Gr^{\sf th} = G(\CC\xT[t^{-1}])/G(\CC[t])$. It is described in modular terms by
    $$
        \Grth = \{ (P, \varphi) : \text{$V$ is a rank $m$ vector bundle on $ \PP $, $\varphi : V \rightarrow V_0 $ on $ D_\infty $ } \} % (a disk centered at $ \infty$)
    $$
    where $D_\infty$ denotes a disk centered at $ \infty$.
    We also have a lattice description 
$$ 
\Gr^{\sf th} = \{ L \subset  \CC((t^{-1}))^m : \text{ $L$ is a $\CC[t]$-lattice} \}
$$   
\jcom{Maybe write $\cK_\infty$ for $ \CC\xT[t^{-1}] $?  Also maybe change the ``thick'' notation''.}

    \item The (two point) Beilinson--Drinfeld Grassmannian $\pi : \Grbd\to \AA$ (with one point fixed at 0, and the second point $s$).
    It is described in modular terms by
    {\small
    $$
    \Grbd = 
    % \begin{aligned}
        \left\{ 
            (V,\varphi,s) : V\text{ is a rank $m$ vector bundle on }\PP, \varphi : V \rightarrow V_0 \text{ on } \PP \setminus \{0, s\}  
        \right\} 
    % \end{aligned}
    $$}
    The fibre of $\Grbd \to \AA$ over $ s \in \AA $, for $ s \ne 0$, will be denoted $ \Gr_{0,s} $ and is given by
    $$ \Gr_{0,s} := \pi^{-1}(s) = G(\CC[t, t^{-1}, (t-s)^{-1}]/G(\CC[t])$$

    We also have a lattice descriptions 
    {\small
    \begin{gather*}
    \Grbd = 
    \{ L \subset  \CC(t)^m, s \in \CC : \text{ $L$ is a $\CC[t]$-lattice 
    % , $L$ is 
    trivial at any $ a \ne 0, s$} \} \\
     \Gr_{0,s} = 
    \{ L \subset  \CC[t,t^{-1},(t-s)^{-1}]^m : \text{ $L$ is a $\CC[t]$-lattice} \}
    \end{gather*} }
    % 
    \item The positive part $ \Gr^+$ of the affine Grassmannian and of the thick affine Grassmannian ${\Grth}^+$ is defined as
    $$
    \Gr^+ = (M_m(\cO) \cap G(\cK)) / G(\cO) \quad {\Grth}^+ = (M_m(\CC[t]) \cap G(\CC((t^{-1}))) / G(\CC[t]) $$
    In modular terms, $\Gr^+$ (resp. ${\Grth}^+$) is the set of those $ (V, \varphi)$, where $ \varphi : V \rightarrow V_0 $ extends to an inclusion of coherent sheaves over $ D_0 $ (resp. over $ \PP$).  In lattice terms, $ \Gr^+$ (resp. ${\Grth}^+$) contains those lattices $L$ which are contained in the standard lattice $ L_0$, i.e. $ L \subseteq L_0$.
\end{itemize}

These different versions of the affine Grassmannian are related as follows.

First there is an isomorphism $ \Gr \cong \Gr_s $ coming from the isomorphism $ \cK \cong \Ks$.

Second, we have a map $$ \Grbd \rightarrow \Grth $$ which is given in modular terms by restricting the trivialization to $ D_\infty$.  It is given in group-theoretic terms on the fibre over $ s $ by
$$
G(\CC[t, t^{-1}, (t-s)^{-1}])/ G(\CC[t]) \rightarrow G(\CC((t^{-1}))/G(\CC[t])
$$
Finally, it is given in lattice terms as the identity on the lattice and using the inclusion $\CC[t, t^{-1}, (t-s)^{-1}]^m \rightarrow \CC((t^{-1}))^m$ on the ambient spaces.

The fibres $ Gr_{0,s}$ of $ \Grbd \rightarrow \AA$ are given as follows
$$
\Gr_{0,s} \cong \begin{cases} \Gr \times \Gr_s, \  s \ne 0 \\
\Gr, \ s = 0.
\end{cases}
$$
This isomorphism is given in the lattice realization as
$$
L \mapsto (L(0), L(s))
$$
in the $ s \ne 0 $ case.
\jcom{Maybe we should introduce some notation for this isomorphism.}

@@

\jcom{I thought that it would be good to introduce this operation now, since we will use it often in the paper and it is the most convenient way to define $Gr^{\lambda_1, \lambda_2}$. I don't know what notation we should use.}

Now fix effective dominant weights $ \lambda_i, \mu_i \in P_{++}$ of size $N_i$ ($i=1,2$) and their sum $ \lambda = \lambda_1 + \lambda_2 = \mu_1 + \mu_2$ of size $ N = N_1 + N_2$.

% 
\begin{itemize}
    % \item Weights $\mu_i\le\lambda_i$ of size $N_i$ ($i=1,2$) 
    % \item Their sums $\mu = \sum \mu_i \le \lambda = \sum\lambda_i$ of size $N = \sum N_i$
    \item The point $L_\lambda = t^\lambda G(\cO)$ in $\Gr$.  In the lattice model, we have
    $$ L_\lambda = span_\cO(t^{\lambda_1}e_1, \dots, t^{\lambda_m}e_m) $$.
    \item The orbit $\Gr^\lambda = G(\cO) L_\lambda$ and its closure $ \overline{\Gr}^\lambda = \cup_{\lambda' \le \lambda} \Gr^{\lambda'}$.  This orbit lies inside the positive part $ \Gr^+$ of the affine Grassmannian.
    \item The family $ \overline{\Gr}^{\lambda_1, \lambda_2} \rightarrow \AA$, defined by $ \overline{\Gr}^{\lambda_1, \lambda_2} = \overline{Gr}^{\lambda_1} * \overline{Gr}^{\lambda_2}$.  By construction the fibre $ \overline{\Gr}_{0,s}^{\lambda_1, \lambda_2} $ over $ s \ne 0 $ is $ \overline{\Gr}^{\lambda_1} \times \overline{\Gr}^{\lambda_2}$.  By Zhu's theorem (\jcom{need ref}), the fibre over $ 0 $ is $ \overline{\Gr}^{\lambda_1 + \lambda_2}$.

    Suppose that $ s \ne 0$.  In the fibre $\overline{\Gr}_{0,s}^{\lambda_1, \lambda_2}$ we have the open locus $ \Gr_{0,s}^{\lambda_1, \lambda_2}$ coming from transporting $ \Gr^{\lambda_1} \times \Gr^{\lambda_2} $ via the isomorphism $ \Grbd_{0,s} \cong \Gr \times \Gr_s $.  This open locus is a $ G(\CC[t])$ orbit.  The lattice description of $ \Gr_{0,s}^{\lambda_1, \lambda_2}$ is given in Lemma \ref{le:Grl1l2} below.

    \item The locus $\cW_\mu = G_1[[t^{-1}]]L_\mu \subset \Grth $.  In modular terms, this corresponds to the locus of those $ (V, \varphi)$ such that $ V $ is isomorphic to the trivial vector bundle on $ \PP$ and such that $ \varphi$ preserves the Harder-Narasimhan filtration at $ \infty$.  The lattice description of $ \cW_\mu \cap \Grth^+$ is given in Lemma \ref{le:Wmu} below.

    \item The semiinfinite orbit $ S^\mu = N(\cK)L_\mu \subset \Gr $.  
    \item The family of semiinfinite orbits $ S^{\mu_1, \mu_2}_\AA := S^{\mu_1} * S^{\mu_2}$.  If $ s \ne 0 $, then the fibre $S^{\mu_1, \mu_2}_{0,s} $ is given by
    $$
    S^{\mu_1, \mu_2}_{0,s} = N(\CC[t, t^{-1}, (t-s)^{-1}])t^{\mu_1} (t-s)^{\mu_2}
    $$
    On the other hand, if $ s = 0$, then the fibre $S^{\mu_1, \mu_2}_{0,0} $ equals $ S^\mu$.

    \jcom{These two statements here require some proof, so perhaps they should be split off as a lemma in ``Rising action''.}

\end{itemize}

\subsection{Matrices}
We now consider some subvarieties of the space of $ N$x$N$ matrices.

%Recall that $ \lambda$ is a partition of $N$ and $ \lambda_1, \lambda_2 $ are partitions of $ N_1, N_2$ with $N_1 + N_2 = N$.

\begin{itemize}
    \item For $ s \in \CC$, we have a Jordan form matrix $ J_{s,\lambda}$ with eigenvalue $ s$ and Jordan blocks of sizes $ \lambda_1, \dots, \lambda_m$.
    \item The adjoint orbit $ \OO^\lambda \subset M_N(\CC)$ of matrices conjugate to $ J_{0,\lambda}$.  Its closure is $ \overline{\OO}^\lambda = \cup_{\lambda' \le \lambda} \OO^{\lambda'}$
    \item For $ s \in \CC, s \ne 0$, the adjoint orbit $ \OO^{\lambda_1, \lambda_2}_{0,s}$ of matrices conjugate to $ J_{0,\lambda_1} \oplus J_{s,\lambda_2}$.  Its closure is $ \overline{\OO}^{\lambda_1, \lambda_2}_{0,s} = \cup_{\lambda_1' \le \lambda_1, \lambda'_2 \le \lambda_2} \OO^{\lambda_1', \lambda'_2}_{0,s}$

    \item A linear operator $ T : V \rightarrow V $ on an $N$-dimensional vector space is said to have Jordan type $(0,\lambda_1), (s,\lambda_2)$ if its matrix representatives lies in $ \OO^{\lambda_1, \lambda_2}_{0,s}$
    \item The family of adjoint orbits $ \overline{\OO}^{\lambda_1, \lambda_2} \rightarrow \AA$ whose fibre over $ s \ne 0 $ is $ \overline{\OO}^{\lambda_1, \lambda_2}_{0,s}$ and whose fibre over 0 is $\overline{\OO}^\lambda$.  \jcom{We should justify why the 0 fibre is correct scheme-theoretically.}

    \item The Mirkovic-Vybnornov slice $\TT_\mu$.  \jcom{Anne, can you add this definition?}

    To each $ A \in \TT_\mu$, we will associate an $m$\times$m$ matrix of polynomials $ g(A) = \left( g(A)_{ij} \right) \in M_m(\CC[t]) $ as follows.
       \begin{equation}
            g(A)_{ij} = \begin{cases} t^{\mu_i} - \sum_{k=1}^{\mu_i} A^k_{ji} t^{k-1} \text{ if $ i = j$} \\
             - \sum_{k=1}^{\mu_i} A^k_{ji} t^{k-1} \text{ if $ i \ne j$ }
        \end{cases}
    \end{equation}
    where $A^k_{ji}$ is the $k$th entry from the left of the last row of the $\mu_j\times\mu_i$ block of $A$. 
\jcom{I moved the definition here since it will be useful for defining the upper triangular stuff.}

    \item The ``upper-triangular'' MVy slice $\TT^{\mu_1, \mu_2,+}_\AA \rightarrow \AA $, defined by
    $$
    \TT^{\mu_1, \mu_2,+}_\AA := \{ (A,s) \in \TT_\mu \times \AA : g(A)_{ii} = t^{\mu_{1,i}} (t-s)^{\mu_{2,i}}, g(A)_{ij} = 0 \text{ for $ j < i $ }\}
    $$
    So a matrix in $\TT^{\mu_1, \mu_2,+}_\AA  $ is weakly block upper-triangular and its diagonal blocks are given by the companion matrices for the polynomials $t^{\mu_{1,i}} (t-s)^{\mu_{2,i}}$.

    Note that the fibre $  \TT^{\mu_1, \mu_2,+}_{0,0}$ is the same as the intersection of $ T^\mu $ with the strictly upper triangular matrices.

    \jcom{Instead of $\TT^+$ maybe a different letter would be best?  I'm moved all $\lambda, \mu$ to upper indices for consistency (except for $ \cW_\mu, T_\mu$) and also to let us put $ s $ or $ \AA$ in the lower index.  I haven't been very consistent about $ \AA $ vs $ \CC$.  Which do you prefer?}
\end{itemize}

\subsection{Old stuff}
\jcom{I'm going to delete everything below here in this section, if that is ok with you.}

@@

\begin{lemma} \label{le:Grl1l2}
    Let $ L \in \Grth^+ $.  Let $ s \in \AA, s \ne 0 $.  The following are equivalent:
    \begin{enumerate}
        \item $ L $ is in the image of the map $ \Gr^{\lambda_1, \lambda_2}_s \rightarrow \Grth^+$
        \item $ L \in G(\CC[t]) t^{\lambda_1} (t-s)^{\lambda_2}$
        \item The linear operator $ t $ on $ L_0/L$ has Jordan type $(0,\lambda_1), (s,\lambda_2)$.
    \end{enumerate}
\end{lemma}

\begin{lemma} \label{le:Wmu}
    Let $ L \in \Grth^+$.  The following are equivalent:
    \begin{enumerate}
        \item $ L \in \cW_\mu$.
        \item $ \{ [t^k e_i] : 0 \le k < \mu_i, 1 \le i \le m\}$ forms a basis for $ L_0/L$.
    \end{enumerate}
\end{lemma}

Since the above basis will occur often, we will denote it  $ \beta_\mu$.

\begin{lemma}
    Under the map $ \Grbd \rightarrow \Grth$, the image of $ S^{\mu_1, \mu_2}_\AA$ lands in $ \cW_\mu$.
\end{lemma}

@@

\begin{theorem} 
The map $ T_\mu \rightarrow \Grth^+ \cap \cW_\mu $ given by $ A \mapsto g(A) $ is an isomorphism with inverse given by
$$ L \mapsto [t|_{L_0/L} ]_{\beta_\mu}$$
\end{theorem}

\jcom{Do we have a reference?}

For the next result, we will consider the ``intersection'' of $ \overline{\Gr}^{\lambda_1, \lambda_2}_\AA $ with $\cW_\mu$.  As $  \overline{\Gr}^{\lambda_1, \lambda_2}_\AA $ is not a subscheme of $ \Grth$ by this intersection, we really mean the preimage of $ \cW_\mu$ under the map $$ \overline{\Gr}^{\lambda_1, \lambda_2}_\AA  \hookrightarrow \Grbd \rightarrow \Grth$$
This is not a very serious abuse of notation, since the map $ \Grbd \rightarrow \Grth $ is almost injective.

In a similar way, we will write $ \overline{\OO}^{\lambda_1, \lambda_2}_\AA \cap T^\mu$, using the non-injective map $ \overline{\OO}^{\lambda_1, \lambda_2}_\AA \rightarrow M_N(\CC)$ (for example the fibre of this map over $ 0 $ is $ \CC $).

\begin{theorem} \label{th:OGrl}
    There is an isomorphism
    $$\overline{\OO}^{\lambda_1, \lambda_2}_\AA \cap T_\mu \cong \overline{Gr}^{\lambda_1, \lambda_2}_\AA \cap \cW_\mu $$
    given by $ (A,s) \mapsto (g(A), s)$.
\end{theorem}

\begin{theorem}
    The isomorphism from Theorem \ref{th:OGrl} restricts to an isomorphism
    $$ \overline{\OO}^{\lambda_1, \lambda_2}_\AA \cap T^{\mu_1, \mu_2, +}_\AA \cong \overline{Gr}^{\lambda_1, \lambda_2}_\AA \cap S^{\mu_1, \mu_2}_\AA$$
\end{theorem}
